Developing Decarbonisation Pathways for Irish homes in changing TIMES

### 2021-08-17 manuscript.tex
Got rid of errors - references OK.

%% 
%% Copyright 2007-2020 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 
%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references
%\usepackage{cite}
%\usepackage{harvard}
%\usepackage{biblatex}
%\usepackage[backend=biber]{biblatex}
% \addbibresource{references.bib} %Imports bibliography file

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
%\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[preprint]{elsarticle}

\usepackage{lineno,hyperref}
\modulolinenumbers[5]

%% `Elsevier LaTeX' style
%\bibliographystyle{elsarticle-num}
%\documentclass[10pt,final,journal,compsoc,a4paper]{IEEEtran}
%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%%\documentclass[final,1p,times,authoryear]{elsarticle}
%% \documentclass[final,1p,times,twocolumn,authoryear]{elsarticle}
%%\documentclass[final,3p,times,authoryear]{elsarticle}
%%\documentclass[final,3p,times,twocolumn,authoryear]{elsarticle}
%% \documentclass[final,5p,times,authoryear]{elsarticle}
%% \documentclass[final,5p,times,twocolumn,authoryear]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{pifont}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{pgf-pie}
\usepackage{pgfplots}
\usepackage{calc}
\usepackage{graphicx}
\usepackage{float}
\usepackage{anyfontsize}
\usepackage{pgfplots}
\usepackage{comment}
\usepackage{booktabs}
\usepackage{rotating}
\usepackage{siunitx}
\usepackage{eurosym}
\usepackage{multirow}
\usepackage{xcolor} 
\usepackage{colortbl}
\usepackage{subcaption}
\usepackage{blindtext}

\DeclareSIUnit{\EUR}{\text{\euro}}
 \pgfplotsset{compat=1.17}
%\usepackage[table]{xcolor}
%\usepackage[backend=bibtex]{biblatex}

%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}
%\bibliographystyle{elsarticle-num}
%\usepackage{cleveref}
%\usepackage{hyperref}
%\usepackage[style=numeric, sorting=none]{biblatex}  %backend=biber is 'better'
%
\addbibresource{TIM_V11.bib}
%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.

\journal{Energy and Buildings}
%\bibliographystyle{elsarticle-num}

@@

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \affiliation for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%            addressline={}, 
%%            city={},
%%            postcode={}, 
%%            state={},
%%            country={}}
%% \fntext[label3]{}

@@

\author[inst1,inst2]{Jason Mc Guire \corref{j.mcguire@ucc.ie}}
\cortext[j.mcguire@ucc.ie]{j.mcguire@ucc.ie}
%footnote{E-mail: \url{j.mcguire@ucc.ie}}}

%\footnote{Contact: j.mcguire@ucc.ie}}
%\thanks{Email: \url{j.mcguire@ucc.ie}}}
\affiliation[inst1]{organization={Energy Policy and Modelling Group, MaREI Centre},%Department and Organization
            addressline={Environmental Research Institute}, 
            city={Cork},
            country={Ireland}}

\affiliation[inst2]{organization={School of Engineering},%Department and Organization
            addressline={University College Cork}, 
            city={Cork},
            country={Ireland}}

@@

\begin{abstract}
%% Text of abstract

@@

@@

%% \linenumbers

%% main text
\section{Introduction}
\label{sec:Introduction}

@@

\subsection{Energy Systems Optimisation Modelling and the Residential Sector}
\label{Intro:ESOM}

@@

Space and water heating are the main energy services, accounting for 80 \% of the energy used in residential dwellings \cite{SustainableEnergyAuthorityofIreland2018EnergySector} and typically have a lifetime of at least 15 years, consequently leading to a slow turnover of technology in the residential sector. Apart from space and water heating, all EU member states are required under commission regulation (EU) 431/2014 to supply energy consumption data on space cooling, cooking, lighting \& appliances, and others (mainly outdoor appliances), the annual trend of these energy services is shown in Figure \ref{fig:IrelandServiceDemands}. These energy services were also used in TIM, however there is no space cooling data in Ireland and lighting \& appliances were separated while others was combined with appliances.

@@

Where t is the type of retrofit. ${TIM_{r,a}}$ is the number of dwellings by rating and archetype and ${TIM_{a}}$ is the total number of dwellings of that archetype.The expected savings from each type of retrofit and for each archetype are outlined in Table \ref{Table:RetrofitSavings}.

@@

\section{Acknowledgements}
\label{sec:Acknowledgements}
The authors wish to acknowledge the contributions of Tomás Mac Uidhir, who supported filtering of the BER database, and Ankita Singh Gaur who developed the residential demands. 
CAPACITY is funded under the Climate Action Modelling Group (CAMG) by DECC.
Alessandro and Maurizio provided technical assistants on the development of the residential sector in TIMES. 
% https://www.marei.ie/project/capacity/
%CHIMERA is supported by a research grant from Science Foundation Ireland (SFI) and the National Natural Science Foundation of China (NSFC) under the SFI-NSFC Partnership Programme, grant no. 17/NSFC/5181 and
%supported by MaREI, the SFI Research Centre for Energy, Climate, and Marine [Grant No: 12/RC/2302\_P2]

@@

\printbibliography
%\bibliography{TIM_V1.1}
%\bibliographystyle{elsarticle-num}
%\bibliography{TIM_V11}
%\bibliographystyle{elsarticle-harv}

%\bibliography{references.bib}

%% else use the following coding to input the bibitems directly in the
%% TeX file.

%%\begin{thebibliography}{00}

% %% \bibitem[Author(year)]{label}
% %% Text of bibliographic item

% \bibitem[ ()]{}

% \end{thebibliography}
\end{document}
%\endinput
%%
%% End of file `elsarticle-template-harv.tex'.

>>>>

\documentclass[final,3p,sort&compress,12pt]{elsarticle}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{pifont}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{pgf-pie}
\usepackage{pgfplots}
\usepackage{calc}
\usepackage{graphicx}
\usepackage{float}
\usepackage{anyfontsize}
\usepackage{pgfplots}
\usepackage{comment}
\usepackage{booktabs}
\usepackage{rotating}
\usepackage{siunitx}
\usepackage{eurosym}
\usepackage{multirow}
\usepackage{xcolor} 
\usepackage{colortbl}
\usepackage{subcaption}
\usepackage{blindtext}

\bibliographystyle{elsarticle-num-names}

\DeclareSIUnit{\EUR}{\text{\euro}}
 \pgfplotsset{compat=1.17}

\journal{Energy and Buildings}

@@

@@

\author[inst1,inst2]{Jason Mc Guire \corref{j.mcguire@ucc.ie}}
\cortext[j.mcguire@ucc.ie]{j.mcguire@ucc.ie}

\affiliation[inst1]{organization={Energy Policy and Modelling Group, MaREI Centre},
            addressline={Environmental Research Institute}, 
            city={Cork},
            country={Ireland}}

\affiliation[inst2]{organization={School of Engineering},
            addressline={University College Cork}, 
            city={Cork},
            country={Ireland}}

@@

 \onehalfspacing
\begin{abstract}
%% Text of abstract

@@

\vspace{0.25cm}
\noindent

@@

%% \linenumbers
\newpage
%% main text
 \onehalfspacing
\section{Introduction}
\label{sec:Introduction}

@@

 \onehalfspacing
\subsection{Energy Systems Optimisation Modelling and the Residential Sector}
\label{Intro:ESOM}

@@

Space and water heating are the main energy services, accounting for 80\% of the energy used in residential dwellings \cite{SustainableEnergyAuthorityofIreland2018EnergySector} and typically have a lifetime of at least 15 years, consequently leading to a slow turnover of technology in the residential sector. Apart from space and water heating, all EU member states are required under commission regulation (EU) 431/2014 to supply energy consumption data on space cooling, cooking, lighting \& appliances, and others (mainly outdoor appliances), the annual trend of these energy services is shown in Figure \ref{fig:IrelandServiceDemands}. These energy services were also used in TIM, however there is no space cooling data in Ireland and lighting \& appliances were separated while others was combined with appliances.

@@

Where t is the type of retrofit. ${TIM_{r,a}}$ is the number of dwellings by rating and archetype and ${TIM_{a}}$ is the total number of dwellings of that archetype. The expected savings from each type of retrofit and for each archetype are outlined in Table \ref{Table:RetrofitSavings}.

@@

\section{Acknowledgements}
\label{sec:Acknowledgements}
The authors wish to acknowledge the contributions of Tomás Mac Uidhir, who supported filtering of the BER database, and Ankita Singh Gaur who developed the residential demands. 
CAPACITY is funded under the Climate Action Modelling Group (CAMG) by DECC.
Alessandro and Maurizio provided technical assistance on the development of the residential sector in TIMES. 
% https://www.marei.ie/project/capacity/
%CHIMERA is supported by a research grant from Science Foundation Ireland (SFI) and the National Natural Science Foundation of China (NSFC) under the SFI-NSFC Partnership Programme, grant no. 17/NSFC/5181 and
%supported by MaREI, the SFI Research Centre for Energy, Climate, and Marine [Grant No: 12/RC/2302\_P2]

@@

\bibliography{TIMref.bib}

\end{document}
%\endinput
%%
%% End of file `elsarticle-template-harv.tex'.
